A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-13 manuscript.Rmd
beauty corrections for the code

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
author: Aaron Peikert and Andreas M. Brandmaier 
output: bookdown::pdf_document2
repro:
  packages:
    - tidyverse
    - usethis
    - gert
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
    - targets
    - renv
    - slider
    - patchwork
  scripts:
    - R/simulation.R
    - R/simulation_funs.R
    - R/link.R
csl: apa7.csl
numbered_headings: true
bibliography: ["references.bib", "packages.bib"]
---

@@

@@

```{r}
generate_data
```

@@

```{r}
planed_analysis
extract_results
```

@@

```{r}
simulation_study
```

>>>>

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
author: Aaron Peikert and Andreas M. Brandmaier 
output: bookdown::pdf_document2
repro:
  packages:
    - tidyverse
    - usethis
    - gert
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
    - targets
    - renv
    - slider
    - patchwork
    - knitr
  scripts:
    - R/simulation.R
    - R/simulation_funs.R
    - R/link.R
csl: apa7.csl
numbered_headings: true
bibliography: ["references.bib", "packages.bib"]
---

@@

```{r}
# define a ürint method for objects of the class data.frame
knit_print.data.frame = function(x, ...) {
  res = paste(c('', '', kable(x)), collapse = '\n')
  asis_output(res)
}
# register the method
registerS3method("knit_print", "data.frame", knit_print.data.frame)
```

@@

```{r generate_data}
```

@@

```{r planed_analysis}
```

```{r extract_results}
```

@@

```{r simulation_study}
```
